\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/algorithm.tex
paper: removed proof and replaced with paragraph

>>>>

While $\textsc{Loss}$ is not monotonically increasing in our model, we maintain a collection of sound and complete Pareto frontiers by 
computing these specific to each dirty set. That is to say, that the combination of $\textsc{Loss}(p) \times \textsc{Dirty}(p)$ for some
plan $p$ behaves monotonically, as the dirty-set is strictly decreasing through the application of $\delta, \mu$ operations. 
The final Pareto frontier corresponds to the collection of plans associated with the empty dirty set.
